\documentclass[a4paper, 11pt]{article}
\title{Paolo Lammens - CV}
\author{Paolo Lammens}

% ----- PACKAGES -----
% input encoding
%\usepackage[utf8]{inputenc}

% page layout
\usepackage[margin=1.5cm]{geometry}

%font
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

%other
\usepackage{longtable}
\usepackage{tabu}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{setspace}

\usepackage{array}
\usepackage{tikz}
    \usetikzlibrary{calc}
\usepackage{fontawesome}
\usepackage{marvosym}
\usepackage{ifthen}
\usepackage{paracol}

\usepackage{hyperref}


% ---------- GLOBAL CONFIGURATION ----------

\newcommand{\cvcolumnratio}{0.25}
\setlength{\parindent}{0pt}

% --- Colours ---
\definecolor{myorange}{rgb}{0.85, 0.4, 0}
\definecolor{primary}{HTML}{723C1F}
\definecolor{secondary}{HTML}{D38806}
\definecolor{highlight}{HTML}{3CA49D}

% --- Hyperref ---
\hypersetup{
    colorlinks,
    linkcolor=primary,
    urlcolor=secondary,
    filecolor=highlight
}

\titlespacing*{\section}{0pt}{0pt}{0pt}
\titlespacing*{\subsection}{0pt}{0pt}{0pt}

\newcommand\icon[1]{\tikz[baseline=(char.base)]{
        \node[shape=circle,draw,inner sep=1pt, fill=myorange,myorange,text=white] (char) {#1};}}
    

% --- Two column environment ---
\def\colratio{0.2}
\def\colsep{10pt}

\newenvironment{twocol}{%
    \columnratio{\colratio}%
    \setlength{\columnsep}{\colsep}% using the default length
    \begin{sloppypar}%
        \begin{paracol}{2}%
}{%
            \bigskip
        \end{paracol}%
    \end{sloppypar}%
}


\begin{document}


% ---------- FORMATTING ----------
\makeatletter

% --- UTILITIES ---
\newcommand{\ifnn}[2]{\ifthenelse{\equal{#1}{}}{}{#2}}
\newcommand{\showlink}[2][https]{\href{#1:#2}{#2}}

% --- CONTACT INFO ---
\newcommand{\rendercvemail}{\href{mailto:\cvemail}{\cvemail}}
\newcommand{\rendercvphone}{\textcolor{myorange}{\cvphone}}
\newcommand{\rendercvlinkedin}{\showlink{linkedin.com/in/\cvlinkedin/}}
\newcommand{\rendercvgithub}{\showlink{github.com/\cvgithub}}
\newcommand{\rendercvstackoverflow}{\showlink{stackoverflow.com/story/\cvstackoverflow}}

% --- SECTIONS ---
\newcommand{\cvsectiontitle}[1]{
    \rule{5mm}{0.5mm}\vspace{2mm}
    \section*{\Large\bfseries #1}
}

\newcommand{\cvsectionrule}{\rule{\columnwidth}{0.5mm}\vspace*{5pt}}

\newcommand{\cvchronoitem}[6]{
    {\raggedright\textbf{#1}\ifnn{#2}{ -- #2}\par}
    \textcolor{myorange}{\small\uppercase{#3 \ifnn{#4}{-- #4} \ifnn{#5}{$\,|\,$ #5}}}
    \medskip\par
    {\setstretch{0.9}\small #6 \par}
}

\newcommand{\cvsoftwareskills}{}
\newcommand{\addcvsoftwareskill}[2]{
    \g@addto@macro\cvsoftwareskills{\\ #1 \noexpand& #2}
}

\newcommand{\cvlanguages}{}
\newcommand{\addcvlanguage}[2]{
    \g@addto@macro\cvlanguages{\\ #1 \noexpand& #2}
}

% global format settings
\hyphenpenalty=10000
\setlength{\tabulinesep}{5pt}
\setlength{\tabcolsep}{10pt}
\thispagestyle{empty}

\setlength{\intextsep}{0.1mm}

\makeatother


% ---------- CONTENT ----------
\newcommand{\cvemail}{lammenspaolo@gmail.com}
\newcommand{\cvphone}{+34 634412833}
\newcommand{\cvlinkedin}{PaoloLammens}
\newcommand{\cvgithub}{plammens}
\newcommand{\cvstackoverflow}{plammens}

\newcommand{\cvaboutme}{\input{modules/aboutme.tex}}

\addcvsoftwareskill{Python}{Fluent}
\addcvsoftwareskill{C++}{Intermediate}
\addcvsoftwareskill{Java}{Intermediate}
\addcvsoftwareskill{Git}{Advanced}
\addcvsoftwareskill{\texttt{numpy}/\texttt{pandas}}{Advanced}
\addcvsoftwareskill{\LaTeX{}}{Lower intermediate}


\addcvlanguage{English}{CEFR C1 (\textit{Cambridge Advanced English certificate})}
\addcvlanguage{Spanish}{Native}
\addcvlanguage{Catalan}{Native}
\addcvlanguage{Italian}{Native}
\addcvlanguage{French}{CEFR A2 (\textit{Diplôme d'Etudes en Langue Francaise})}



% ------------- TYPESET -------------


\begin{twocol}
    {\huge\textbf{Paolo Lammens}}
    
    \switchcolumn
    
    {\setlength{\tabcolsep}{0pt}
    \begin{tabular}{p{8mm}p{6cm}p{8mm}p{4cm}}%
        \icon{@} & \rendercvemail & \icon{\faGithub} & \rendercvgithub \\
        \Large\icon{\Telefon} & \rendercvphone & \icon{\faStackOverflow} & \rendercvstackoverflow \\
        \icon{\faLinkedin} & \rendercvlinkedin & &
    \end{tabular}}
    \vspace*{10pt}\newline
    \subsection*{About me}
    \cvaboutme
\end{twocol}
    
\begin{twocol}
    \cvsectiontitle{Education}
    
    \switchcolumn
    
    \cvsectionrule
    \cvchronoitem{\textbf{Mathematics \& Computing Science, MSci}}
                 {University of Glasgow}
                 {september 2019}{present}{expected graduation year: 2023}
                 {Activities \& Societies: GU Tech Society, HackerOlympics 2019, Chapel Choir, Kelvin Ensemble, Dialectic Society, GU Debates. \textit{GPA: 19 (out of 22)}}
    \bigskip
    \cvchronoitem{\textbf{Mathematics \& Data Science}}
                 {Centre de Formació Interdisciplinària Superior (CFIS) at Univ. Politècnica de Catalunya (UPC)}
                 {September 2018}{may 2019}{discontinued}
                 {Double degree programme offered by CFIS in Mathematics and Data Science. The study of mathematics \& computer science has been continued at the University of Glasgow. \textit{Average grade: 8.12/10}}
\end{twocol}


\begin{twocol}
    \cvsectiontitle{Work experience}
    
    \switchcolumn
    
    \cvsectionrule
    \cvchronoitem{\textbf{Python tutor}}
    {Freelance}
    {March 2020}{present}{}
    {Python lessons and one-off project help. Advertised through Superprof and other online platforms: \href{https://www.superprof.co.uk/msci-maths-comp-sci-student-offering-online-python-java-programming-support.html}{superprof.co.uk/msci-maths-comp-sci-student-offering-online-python-java-programming-support.html}.}
\end{twocol}
     
\begin{twocol}
     \cvsectiontitle{Software\\skills}
     
     \switchcolumn
     
     \cvsectionrule\newline
     \begin{tabular}{p{3cm}|p{6cm}}
          \large \textbf{Technology} & \large \textbf{Skill level}
          \cvsoftwareskills
     \end{tabular}
\end{twocol}

\begin{twocol}
    \cvsectiontitle{Courses}
    
    \switchcolumn
    
    \cvsectionrule
    \cvchronoitem{MESIO Summer School 2019}
                 {Univ. Politèc. de Catalunya - Univ. de Barcelona}
                 {June}{July 2019}
                 {}
                 {The MESIO (Master in Statistics and Operations Research) UPC-UB Summer School is a specialized training program that offers several 15-hour courses in the span of four weeks, with topics ranging from statistics to deep learning. I attended the following courses:
                     \begin{itemize}
                         \item \textbf{Statistical and Machine Learning Methods for Classification Using R} -- this course presented a range of statistical methods and models for classification, with their implementation in R. \textit{Grade: 9.8/10}
                         \item \textbf{``Curso Práctico de Deep Learning''} -- an overview of deep learning models, and their implementation with Keras in R or Python. \textit{Grade: 9.5/10}
                         \item \textbf{``Deep Learning with PyTorch''} -- introduction to deep learning using the PyTorch library. \textit{Grade: 9/10}
                     \end{itemize}
                 }
     
     \cvchronoitem{Wolfram High School Summer Camp}
                  {Wolfram}
                  {July 2018}{}{}
                  {WHSSC is a two-week program for high school students that involves developing your own project in the Wolfram Language, along with several seminars on computer science and new technologies.}
                  
     \smallskip
     \cvchronoitem{“Bojos per la Ciència”}
     {Fundació Catalunya - La Pedrera}
     {January 2017}{January 2018}{}
     {Educational program aimed at High School students that want to develop their scientific skills through lectures and practical sessions. Participated in the Biomedicine program.}
     
     \smallskip
     \cvchronoitem{“Joves i Ciència”}
     {Fundació Catalunya - La Pedrera}
     {June 2016}{June 2018}{}
     {Two-year scholarship awarded to 50 Catalan students with a high scientific vocation that includes first-hand participation in research.}
\end{twocol}

\begin{twocol}
     \cvsectiontitle{Projects}
     
     \switchcolumn
     
     \cvsectionrule
     
     \cvchronoitem{Analysing and visualising chord sequences in music}
                  {}
                  {July 2018}{}{archived}
                  {This is the project developed as part of my stay at Wolfram High School Summer Camp. It involved creating a Mathematica script/application that analyses the harmony in music pieces and displays it as a transition graph.
                  Link: \showlink{community.wolfram.com/groups/-/m/t/1383630}}
      \smallskip
      \cvchronoitem{PySimplex}
      {}
      {November 2018}{}{archived}
      {Simple Python implementation of the primal simplex algorithm in linear optimization. Based on university coursework from the Mathematical Programming course. Link: \showlink{github.com/plammens/PySimplex}}
      
      \smallskip
      \cvchronoitem{CENP-C -- Study of a protein}
      {}
      {May}{December 2017}{archived}
      {Research project for the last year of secondary education (“Treball de Recerca”) on a protein found in the chromosomes of most eukaryotic organisms.}
\end{twocol}

\begin{twocol}
     \cvsectiontitle{Languages}
     
     \switchcolumn
     
     \cvsectionrule\newline
     \begin{tabular}{l|l}
         \large \textbf{Language}  & \large \textbf{Skill level}
         \cvlanguages
     \end{tabular}
\end{twocol}

\begin{twocol}
     \cvsectiontitle{Musical education}
     
     \switchcolumn
     
     \cvsectionrule
     \cvchronoitem{\textbf{``Grau Professional de Música''}}
     {``Victòria dels Àngels'' Municipal Music School}
     {october 2010}{june 2018}{}
     {[Junior] conservatoire music education with cello as main instrument.}
\end{twocol}

\end{document}


