\documentclass[]{twentysecondcv}

\usepackage{changepage}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\definecolor{lgray}{gray}{0.3}

 
\begin{document}

%%%%%%%%%%%%%%%%%
%%PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%
%%PERSONAL INFO%%%
%%%%%%%%%%%%%%%%

\cvname{Paolo Lammens} %your name
\cvjobtitle{}%your actual job position
\cvnumberphone{+34 634412833}%telphone number
\cvmail{lammenspaolo@gmail.com}%e-mail
\cvgithub{github.com/plammens}
\cvlinkedin{linkedin.com/in/PaoloLammens}


\aboutme{
Mathematics \& Comp. Sci. student with attested interest in software development, music, and machine learning. Strong in Python.}%About me section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill bar section, each skill must have a value between 0 an 6 (float)%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\skills{{Python/4},{C++/3.5},{LaTeX/3},{R/2},{Mathematica (Wolfram Language)/3},{Git/3.5}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill text section, each skill must have a value between 0 an 6%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvlanguages{
    \normalsize
    \begin{tabular}{p{2cm} L{4cm}}
        English & \textcolor{lgray}{CEFR C1 (\textit{Cambridge Advanced English Certificate})} \\
        Spanish & \textcolor{lgray}{Native} \\
        Catalan & \textcolor{lgray}{Native} \\
        Italian & \textcolor{lgray}{Maternal} \\
        French & \textcolor{lgray}{CEFR A2 (\textit{Diplôme d'Etudes en Langue Française})} \\
    \end{tabular}
}

\cvinterests{
    \begin{itemize}
        \item Music -- \textcolor{lgray}{have been playing the cello since the age of four. Obtained the ``Grau Professional'' from local conservatoire, the ``Escola Municipal de Música Victòria dels Àngels.''}
        \item Open Source Development -- \textcolor{lgray}{have been participating in the \texttt{python-\linebreak{}telegram-bot} GitHub repository.}
    \end{itemize}
}

\makeprofile



%%%%%%%%%%%%%%%%%%%%
%%END PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%BODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%SIMPLE SECTION%%%%%%
%%%%%%%%%%%%%%%%%%%%

\begin{adjustwidth}{10pt}{10pt}

\section*{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%TWENTY LIST ITEMS%%%%%%%%%%%%%%
%%    Four arguments: date; title; where; description %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\twentylen}{11cm}
\begin{twenty}[1.5cm]
  \twentyitem
    {\noindent 2019 - present}
    {\large MSci (Hon.) Mathematics \& Computing Science}
    {University of Glasgow}
    {Entered at Level 2. Activities \& Societies: GU Tech Society, HackerOlympics 2019, Chapel Choir, Kelvin Ensemble, Dialectic Society, GU Debates}
  \twentyitem
    {2018 - 2019}
    {Mathematics \& Data Science (discontinued)}
    {Centre de Formació Interdisciplinària Superior (CFIS) – Universitat Politècnica de Catalunya (UPC)}
    {Double degree programme offered by CFIS in Mathematics and Data Science. The study of mathematics \& computer science has been continued at the University of Glasgow.}
\end{twenty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%TWENTY LIST SHORTITEMS%%%%%%%%%%%%%%
%%% Two arguments: date; title/description %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Projects}

\renewcommand{\twentylen}{9.7cm}
\begin{twenty}[2.8cm]
  \twentyitem
      {November 2018 \\ (archived)}
      {PySimplex}
      {}
      {Simple Python implementation of the primal simplex algorithm in linear optimization. Based on university coursework from the Mathematical Programming course. Link: \href{https://github.com/plammens/PySimplex}{github.com/plammens/PySimplex}}
  \twentyitem
      {July 2018 \\ (archived)}
      {Analysing and visualising chord sequences in music}
      {}
      {This project involved creating a Mathematica/Wolfram Language script that analyses the harmony in music pieces and displays it as a transition graph.}
  \twentyitem
      {May - Dec. 2017 \\ (archived)}
      {CENP-C – Study of a protein}
      {}
      {Research project for the last year of secondary education (“Treball de Recerca”) on a protein found in the chromosomes of most eukaryotic organisms.}
\end{twenty}



\section*{Courses \& programmes}

\renewcommand{\twentylen}{10.2cm}
\begin{twenty}[2.3cm]
    \twentyitem
    {June - July \\ 2019}
    {MESIO Summer School 2019}
    {Universitat Politècnica de Catalunya - Universitat de Barcelona}
    {Attended the following courses:
     \begin{itemize}
         \item \textbf{Statistical and Machine Learning Methods for Classification Using R} -- learned the theoretical framework behind a range of statistical methods and models for classification and implemented them in R. Applied that knowledge to some real-word datasets. \textit{Mark: 9.8/10}
         \item \textbf{''Curso Práctico de Deep Learning''} -- an overview of deep learning models, and their implementation with Keras. Developed and trained a 1-D convolutional model and applied some visualization techniques as the final project. \textit{Mark: 9.5/10}
         \item \textbf{Deep Learning with PyTorch} -- introduction to deep learning using the PyTorch library. Pre-processed a text corpus and trained an RNN on it for text sentiment analysis. \textit{Mark: 9/10}
     \end{itemize}
    }
    \twentyitem
    {July \\ 2018}
    {Wolfram High School Summer Camp}
    {Wolfram}
    {Attended several seminars on computer science and new technologies. Developed the project ``Analysing and visualising chord sequences in music'' using the Wolfram Language.} % TODO: add link
    \twentyitem
    {Jan. 2017 - \\ Jan. 2018}
    {``Bojos per la Biomedicina''}
    {Fundació Catalunya - La Pedrera}
    {Completed a small experiment with one of the research teams at the Institute for Research in Biomedicine (Barcelona) every week, attending an explanatory lecture for each.}
    \twentyitem
    {June 2016 - \\ June 2018}
    {``Joves i Ciència''}
    {Fundació Catalunya - La Pedrera}
    {Three-year scholarship awarded to 50 Catalan students with a high scientific vocation that includes first-hand participation in research. Participated in the genetics project, a stay at the Institute of Photonic Sciences (ICFO), and the Wolfram High School Summer Camp for each of the three years respectively.}
\end{twenty}


\end{adjustwidth}

%%%%%%%%%%%%%%%%%%%%
%%%%%ENDBODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\end{document} 